Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-21 tex/main/manuscript.tex
结果第二部分第一段，及相应的补充材料，图

\section*{Results}
\subsection*{Detection of Water utilization regimes}
% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization) (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while tendentiousness and pattern of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of tendentiousness and pattern of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness (+0.485) and pattern (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is tendentiousness; and P3 is pattern.

@@

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress (Figure~\ref{fig:dimensions}A).
% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
The P1, when water resources were the most abundant period, also had the least water consumption, 
while most of which were flexible water utilization.
Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, which increased storage capacities in each water-demand region to relief water resource stresses (SI).
However, entering P2, although water consumptions continued to increase, 
the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

>>>>

\section*{Results}
\subsection*{Detection of Water utilization regimes}
% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points detected, the trend of IWRU index are split into three periods, whose slopes are various and mainly contributed by different dimensions (stress, tendentiousness or pattern of water utilization, see Methods) (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722), while tendentiousness and pattern of the water utilization had slight negative contribution (-0.048 and -0.09 respectively).
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of tendentiousness and pattern of water utilization (+0.352 and +0.279 respectively), because of increasing stresses on water resource playing a larger negative role (-0.636). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness (+0.485) and pattern (+0.515), and decelerations of water stresses (-0.344, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is tendentiousness; and P3 is pattern.

@@

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress, which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}A and Figure~\ref{fig:dimensions}D).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with lesser water consumptions (supplementary Fig. S1 and S3) and most of which were flexible water utilization (supplementary Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but most of which built in P1 (supplementary Fig. S5 and supplementary Table S1). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}E) and patterns (Figure~\ref{fig:dimensions}C and Figure~\ref{fig:dimensions}F) of water utilization were enlarging their impacts. 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

### 2020-08-21 tex/sup/PNAS-template-main.tex
结果第二部分第一段，及相应的补充材料，图

% \section*{Supplementary Information Methods}
\section*{Methods S1. Definition of study area}
% 黄河经历了水资源开发利用和制度改革
The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig. 1). According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig. 2), which has been widely recognized (ref.). Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig. 3):
\begin{itemize}
    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water conservation, as sparsely populated and less economically developed.
    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region. However, because of backward production methods, efficiency of irrigation are used to be very low.
    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk. To reverse this situation, the grain for green project changed the water utilization here strikingly.
    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region. However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
\end{itemize}

@@

%%% Each figure should be on its own page
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
    \caption{Yellow River Basin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
\caption{Natural measured runoff of Yellow River within different periods.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
\caption{Second figure}
\end{figure}

\begin{table}\centering
\caption{This is a table}

>>>>

% \section*{Supplementary Information Methods}
\section*{Methods S1. Definition of study area}
% 黄河经历了水资源开发利用和制度改革
The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig. 1A). According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig. 1B), which has been widely recognized (ref.). Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig. 2):
\begin{itemize}
    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water conservation, as sparsely populated and less economically developed.
    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region. However, because of backward production methods, efficiency of irrigation are used to be very low.
    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk. To reverse this situation, the grain for green project changed the water utilization here strikingly.
    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region. However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
\end{itemize}

@@

%%% Each figure should be on its own page
% 补充图片1：研究区示意图
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
    \caption{Yellow River Basin}
\end{figure}

% 补充图片2：研究区分区特征
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
    \caption{Different regions}
\end{figure}

% 补充图片3：天然水资源量
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
    \caption{Natural measured runoff of Yellow River within different periods.}
\end{figure}

% 补充图片4：水资源灵活性
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/inflexible_wu.pdf}
    \caption{Flexibility}
\end{figure}

% 补充图片5：水库数量和累积库容
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/reservoirs.pdf}
    \caption{Reservoirs and accumulated storage}
\end{figure}

%% 表格
\begin{table}\centering
\caption{This is a table}
